\ \\ \LARGE\bf Speculative Evaluation in Particle Swarm Optimization \thanks{Matthew Gardner, Andrew McNabb, and Kevin Seppi are with the Department of Computer Science, Brigham Young University, 3361 TMCB, Provo, UT 84602 (phone: 801-422-8717; email: \{mjg82,a,k\}@cs.byu.edu).}

### 2010-03-18 honors_thesis/journal_paper/paper.tex
Fixed the permissions on paper.tex

At each iteration of the algorithm, the position $\ppos_t$ and velocity
$\pvel_t$ of each particle $i$ are updated as follows:
\begin{align}
\label{eq:velupdate}
	\pvel_{i,t+1} &=
		\constriction \left[ \pvel_t +
			\pcoeff\pURand_{i,t}\otimes(\pbest_{i,t} - \ppos_{i,t}) +
			\ncoeff\nURand_{i,t}\otimes(\nbest_{i,t} - \ppos_{i,t})
		\right] \\
\label{eq:posupdate}
	\ppos_{i,t+1} &= \ppos_{i,t} + \pvel_{i,t+1}
\end{align}
where \( \nURand_{i,t} \) and \( \nURand_{i,t} \) are vectors of independent
and identically distributed random numbers drawn from a uniform
distribution, the \( \otimes \) operator is an element-wise vector
multiplication, $\pbest$ (called personal best) is the best position the
current particle has seen, and $\nbest$ (called neighborhood best) is the best
position the neighbors of the current particle have seen.  \( \ncoeff \), \(
\pcoeff \), and \( \constriction \) are parameters with prescribed values
required to ensure convergence (2.05, 2.05, and .73,
respectively)~\cite{clerc-tec02}. Note also that we have made the particle identifier $i$
and the time step $t$ or $t+1$ explicit in the subscript and moved other qualifiers,
such as the personal $\pers$ and personal best $\pers*$ qualifiers to the superscript position.
Superscripts can be miss read as exponents, but they are qualifiers throughout this paper.

@@

\begin{figure}
  \centering
  \psfrag{pt-n}[C][C]{$\nonbest{\p}_{t}$}
  \psfrag{nt-n}[C][C]{$\nonbest{\nset}_{t}$}
  \psfrag{pt}[C][C]{$\p_{t}$}
  \psfrag{pt1-n}[C][C]{$\nonbest{\p}_{t+1}$}
  \psfrag{st1-n}[C][C]{$\nonbest{\sset}_{t+1}$}
  \includegraphics[width=.5\columnwidth]{messages2.eps}
  \caption{The production of $\nonbest{\p}_{t+1}$ from the original particle 
  $\nonbest{\p}_{t}$, messages $\nonbest{\nset}_{t}$ and
  $\nonbest{\sset}_{t+1}$, and intermediate particles.}
  \label{fig:messages2}
\end{figure}

@@

\begin{figure}
  \centering
  \psfrag{nt-n}[C][C]{$\nonbest{\nset}_{t}$}
  \psfrag{nnt-n}[C][C]{$\nonbest{\nnset}_{t}$}
  \psfrag{nt}[C][C]{$\nset_{t}$}
  \psfrag{nt1-n}[C][C]{$\nonbest{\nset}_{t+1}$}
  \psfrag{nst1-n}[C][C]{$\nonbest{\nsset}_{t+1}$}
  \includegraphics[width=.6\columnwidth]{messages3.eps}
  \caption{The production of each $\nonbest{\n}_{t+1}$ from the original
  particle $\nonbest{\n}_{t}$, messages $\nonbest{\nnset}_{t}$ and
  $\nonbest{\nsset}_{t+1}$, and intermediate particles.  $\nnset$ is the set of
  neighbors for each particle $\n$, and $\nsset$ is the set of $\n$'s
  speculative children.  Note the similarity between this and \fig{messages2}.}
  \label{fig:messages3}
\end{figure}

@@

\begin{figure}
  \centering
  \psfrag{pt-n}[C][C]{$\nonbest{\p}_{t}$}
  \psfrag{nt-n}[C][C]{$\nonbest{\nset}_{t}$}
  \psfrag{pt}[C][C]{$\p_{t}$}
  \psfrag{pt1-n}[C][C]{$\nonbest{\p}_{t+1}$}
  \psfrag{st1-n}[C][C]{$\nonbest{\sset}_{t+1}$}
  \psfrag{nt-n}[C][C]{$\nonbest{\nset}_{t}$}
  \psfrag{nnt-n}[C][C]{$\nonbest{\nnset}_{t}$}
  \psfrag{nt}[C][C]{$\nset_{t}$}
  \psfrag{nt1-n}[C][C]{$\nonbest{\nset}_{t+1}$}
  \psfrag{nst1-n}[C][C]{$\nonbest{\nsset}_{t+1}$}
  \psfrag{pt1}[C][C]{$\p_{t+1}$}
  \includegraphics[width=.8\columnwidth]{messages4.eps}
  \caption{The production of $\p_{t+1}$ from the original particle 
  $\nonbest{\p}_{t}$, messages $\nonbest{\nset}_{t}$, $\nonbest{\sset}_{t+1}$,
  $\nonbest{\nnset}_{t}$, and $\nonbest{\nsset}_{t+1}$, and intermediate
  particles.  Note that this is just a combination of \fig{messages2} and
  \fig{messages3}.}
  \label{fig:messages4}
\end{figure}

@@

\begin{figure}
  \centering
  \psfrag{pt1}[C][C]{$\p_{t+1}$}
  \psfrag{nt1}[C][C]{$\nset_{t+1}$}
  \psfrag{nt2-e}[C][C]{$\noeval{\nset}_{t+2}$}
  \psfrag{pt2-e}[C][C]{$\noeval{\p}_{t+2}$}
  \psfrag{st3-e}[C][C]{$\noeval{\sset}_{t+3}$}
  \includegraphics[width=.5\columnwidth]{messages5.eps}
  \caption{The production of $\noeval{\p}_{t+2}$ and $\noeval{\sset}_{t+3}$
  from $\p_{t+1}$ and $\n_{t+1}$, each of which are produced as in
  \fig{messages4}.}
  \label{fig:messages5}
\end{figure}

>>>>

At each iteration of the algorithm, the position $\ppos_t$ and velocity
$\pvel_t$ of each particle $i$ are updated as follows:
\begin{align}
\label{eq:velupdate}
	\pvel_{i,t+1} &=
		\constriction \left[ \pvel_t +
			\pcoeff\pURand_{i,t}\otimes(\pbest_{i,t} - \ppos_{i,t}) +
			\ncoeff\nURand_{i,t}\otimes(\nbest_{i,t} - \ppos_{i,t})
		\right] \\
\label{eq:posupdate}
	\ppos_{i,t+1} &= \ppos_{i,t} + \pvel_{i,t+1}
\end{align}
where \( \nURand_{i,t} \) and \( \nURand_{i,t} \) are vectors of independent
and identically distributed random numbers drawn from a uniform
distribution, the \( \otimes \) operator is an element-wise vector
multiplication, $\pbest$ (called personal best) is the best position the
current particle has seen, and $\nbest$ (called neighborhood best) is the best
position the neighbors of the current particle have seen~\cite{bratton-sis07}.  \( \ncoeff \), \(
\pcoeff \), and \( \constriction \) are parameters with prescribed values
required to ensure convergence (2.05, 2.05, and .73,
respectively)~\cite{clerc-tec02}. Note also that we have made the particle identifier $i$
and the time step $t$ or $t+1$ explicit in the subscript and moved other qualifiers,
such as the personal $\pers$ and personal best $\pers*$ qualifiers to the superscript position.
Superscripts can be miss read as exponents, but they are qualifiers throughout this paper.

@@

\begin{figure}
  \centering
  \psfrag{pt-n}[C][C]{$\nonbest{\p}_{t}$}
  \psfrag{nt-n}[C][C]{$\nonbest{\nset}_{t}$}
  \psfrag{pt}[C][C]{$\p_{t}$}
  \psfrag{pt1-n}[C][C]{$\nonbest{\p}_{t+1}$}
  \psfrag{st1-n}[C][C]{$\nonbest{\sset}_{t+1}$}
  \includegraphics[width=.5\columnwidth]{messages2}
  \caption{The production of $\nonbest{\p}_{t+1}$ from the original particle 
  $\nonbest{\p}_{t}$, messages $\nonbest{\nset}_{t}$ and
  $\nonbest{\sset}_{t+1}$, and intermediate particles.}
  \label{fig:messages2}
\end{figure}

@@

\begin{figure}
  \centering
  \psfrag{nt-n}[C][C]{$\nonbest{\nset}_{t}$}
  \psfrag{nnt-n}[C][C]{$\nonbest{\nnset}_{t}$}
  \psfrag{nt}[C][C]{$\nset_{t}$}
  \psfrag{nt1-n}[C][C]{$\nonbest{\nset}_{t+1}$}
  \psfrag{nst1-n}[C][C]{$\nonbest{\nsset}_{t+1}$}
  \includegraphics[width=.6\columnwidth]{messages3}
  \caption{The production of each $\nonbest{\n}_{t+1}$ from the original
  particle $\nonbest{\n}_{t}$, messages $\nonbest{\nnset}_{t}$ and
  $\nonbest{\nsset}_{t+1}$, and intermediate particles.  $\nnset$ is the set of
  neighbors for each particle $\n$, and $\nsset$ is the set of $\n$'s
  speculative children.  Note the similarity between this and \fig{messages2}.}
  \label{fig:messages3}
\end{figure}

@@

\begin{figure}
  \centering
  \psfrag{pt-n}[C][C]{$\nonbest{\p}_{t}$}
  \psfrag{nt-n}[C][C]{$\nonbest{\nset}_{t}$}
  \psfrag{pt}[C][C]{$\p_{t}$}
  \psfrag{pt1-n}[C][C]{$\nonbest{\p}_{t+1}$}
  \psfrag{st1-n}[C][C]{$\nonbest{\sset}_{t+1}$}
  \psfrag{nt-n}[C][C]{$\nonbest{\nset}_{t}$}
  \psfrag{nnt-n}[C][C]{$\nonbest{\nnset}_{t}$}
  \psfrag{nt}[C][C]{$\nset_{t}$}
  \psfrag{nt1-n}[C][C]{$\nonbest{\nset}_{t+1}$}
  \psfrag{nst1-n}[C][C]{$\nonbest{\nsset}_{t+1}$}
  \psfrag{pt1}[C][C]{$\p_{t+1}$}
  \includegraphics[width=.8\columnwidth]{messages4}
  \caption{The production of $\p_{t+1}$ from the original particle 
  $\nonbest{\p}_{t}$, messages $\nonbest{\nset}_{t}$, $\nonbest{\sset}_{t+1}$,
  $\nonbest{\nnset}_{t}$, and $\nonbest{\nsset}_{t+1}$, and intermediate
  particles.  Note that this is just a combination of \fig{messages2} and
  \fig{messages3}.}
  \label{fig:messages4}
\end{figure}

@@

\begin{figure}
  \centering
  \psfrag{pt1}[C][C]{$\p_{t+1}$}
  \psfrag{nt1}[C][C]{$\nset_{t+1}$}
  \psfrag{nt2-e}[C][C]{$\noeval{\nset}_{t+2}$}
  \psfrag{pt2-e}[C][C]{$\noeval{\p}_{t+2}$}
  \psfrag{st3-e}[C][C]{$\noeval{\sset}_{t+3}$}
  \includegraphics[width=.5\columnwidth]{messages5}
  \caption{The production of $\noeval{\p}_{t+2}$ and $\noeval{\sset}_{t+3}$
  from $\p_{t+1}$ and $\n_{t+1}$, each of which are produced as in
  \fig{messages4}.}
  \label{fig:messages5}
\end{figure}
